Data Responsive-report

### 2021-02-02 GALI_2020.Rmd
rmds

#load libraries
#if (!requireNamespace("BiocManager", quietly = TRUE))
    #install.packages("BiocManager")

@@

library(rio)
library(tidyverse)
library(lubridate)
library(janitor)
library(ggplot2)
library(readxl)
library(reshape2)
library(readr)
library(psych)
library(foreign)
library(plm)
library(lme4)
library(lattice)
library(lmerTest)
library(EFAutilities)
library(haven)
library(sjPlot)
library(XLConnect)
library(preprocessCore)

@@

```{r Clean data from big firms, non-profit, and non respondants to follow-up survey}
gali <- import("GALI CLEANED 2019.xlsx") #19412 obs
gali <- filter(gali, fins_ft_employees_m1 <500 | is.na(fins_ft_employees_m1) ) #19401
gali <- filter(gali, info_legal_status == "For-profit company") #15433
gali <- filter(gali, found_additional_cnt < 10 | is.na(found_additional_cnt))

gali <- filter(gali, found_name1_prior_fp <10 | is.na(found_name1_prior_fp))
gali <- filter(gali, found_name2_prior_fp <10 | is.na(found_name2_prior_fp))
gali <- filter(gali, found_name3_prior_fp <10 | is.na(found_name3_prior_fp))
gali <- filter(gali, found_name1_prior_other <10 | is.na(found_name1_prior_other))
gali <- filter(gali, found_name2_prior_other <10 | is.na(found_name2_prior_other))
gali <- filter(gali, found_name3_prior_other <10 | is.na(found_name3_prior_other))
gali <- filter(gali, found_name1_prior_np <10 | is.na(found_name1_prior_np))
gali <- filter(gali, found_name2_prior_np <10 | is.na(found_name2_prior_np))
gali <- filter(gali, found_name3_prior_np <10 | is.na(found_name3_prior_np))
gali <- filter(gali, found_name1_age > 14 | is.na(found_name1_age))
gali <- filter(gali, found_name2_age > 14 | is.na(found_name2_age))
gali <- filter(gali, found_name3_age > 14 | is.na(found_name3_age))
gali <- filter(gali, found_name1_age < 70 | is.na(found_name1_age))
gali <- filter(gali, found_name2_age < 70 | is.na(found_name2_age))
gali <- filter(gali, found_name3_age < 70 | is.na(found_name3_age))

#gali <- filter(gali, finished == 1 | `fu1-report_any_prior_accelerator` == 1)
#gali$receivedHC <- ifelse(gali$finished == 0 & (gali$`fu1-report_any_prior_accelerator` == 0 | is.na(gali$`fu1-report_any_prior_accelerator`)) , 0, 1 )

#Keep only ventures with post acceleration information 
gali <- filter(gali, `fu1-report_followup_yes` == 1)

@@

#Removing countries with less than 30 ventures.

#First, let's remove the US from the sample, 
gali <- filter(gali, info_venture_country_hq != "United States of America")

@@

countries_to_keep <- filter(countries_to_keep, Count >70)
countries_to_keep$`gali$info_venture_country_hq`

@@

@@

if (gali$application_year == 2013) { gali <- filter(gali, info_founding_year > 2007)
}  else if (gali$application_year == 2014) {gali <- filter(gali, info_founding_year > 2008)
} else if (gali$application_year == 2015) {gali <- filter(gali, info_founding_year > 2009)
}  else if (gali$application_year == 2016) {gali <- filter(gali, info_founding_year > 2010)
} else if (gali$application_year == 2017) {gali <- filter(gali, info_founding_year > 2011)
}  else gali <- filter(gali, info_founding_year > 2012)

@@

#Rnak 1 shows the most important benefit (highest attention)

#Calculating the average of different benifits to group them into one of the 3 categories of capital plus signaling. Then making the range of values between 0 and 1

gali$attention_HC <- round((rowMeans(gali[,
                                  c('accel_ben_rank_business_skills',
                                    'accel_ben_rank_mentorship')],
                              na.rm=TRUE) / 7),2)

gali$attention_signaling <- round((gali$accel_ben_rank_aware_cred / 7),2)

gali$attention_SC <- round((rowMeans(gali[,
                                  c('accel_ben_rank_network',
                                'accel_ben_rank_access_entreprene')],
                              na.rm=TRUE) / 7),2)

gali$attention_FC <- round((rowMeans(gali[,
                                c('accel_ben_rank_access_investors',
                                  'accel_ben_rank_direct_funding')],
                              na.rm=TRUE) / 7),2)

#the lowest the value the highest the attention 
#I will then mutiply this by the country index to measure the congruence level

range(gali$attention_signaling)
```

@@

#Country indices to interact with venture attention and construct conguence level

```{r Merge with GEM NES NATIONAL data}

gem15 <- import("GEM 2015 NES NATIONAL.sav")
gem14 <- import("GEM 2014 NES NATIONAL.sav")
gem13 <- import("GEM 2013 NES NATIONAL.sav")

#GEM Selecting only Human Capital Variables (HC = human capital)

gem_HC15 <-gem15 %>%
  select(NES15COUNTRY, NES15RNAME, NES15_C02_MEAN9, NES15_D01_MEAN9, NES15_D02_MEAN9, NES15_D03_MEAN9, NES15_D04_MEAN9, NES15_D05_MEAN9, NES15_D06_MEAN9, ZNES15D1SUM9, ZNES15D2SUM9,   EU, OECD, BRICS)

gem_HC14 <-gem14 %>%
  select(NES14COUNTRY, NES14RNAME, NES14_C02_MEAN, NES14_D01_MEAN, NES14_D02_MEAN, NES14_D03_MEAN, NES14_D04_MEAN, NES14_D05_MEAN, NES14_D06_MEAN, ZNES14D1SUM, ZNES14D2SUM,   EU, OECD, BRICS)

gem_HC13 <-gem13 %>%
  select(NES13COUNTRY, NES13RNAME, NES13_C02_MEAN, NES13_D01_MEAN, NES13_D02_MEAN, NES13_D03_MEAN, NES13_D04_MEAN, NES13_D05_MEAN, NES13_D06_MEAN, ZNES13D1SUM, ZNES13D2SUM,   EU, OECD, BRICS)

gem <- bind_rows(gem_HC15, gem_HC14, gem_HC13)

gem$NES15RNAME[gem$NES15RNAME == "UK"] <-"UNITED KINGDOM OF GREAT BRITAIN AND NORTHERN IRELAND"

gem$NES15RNAME[gem$NES15RNAME == "NETEHERLANDS"] <- "NETHERLANDS"

gem1 <- bind_rows(gem_HC14, gem_HC15, gem_HC13)

gem1$NES14RNAME[gem1$NES14RNAME == "UK"] <-"UNITED KINGDOM OF GREAT BRITAIN AND NORTHERN IRELAND"
gem1$NES14RNAME[gem1$NES14RNAME == "NETEHERLANDS"] <- "NETHERLANDS"

gem2 <- bind_rows(gem_HC13, gem_HC15, gem_HC14)

gem2$NES13RNAME[gem2$NES13RNAME == "UK"] <-"UNITED KINGDOM OF GREAT BRITAIN AND NORTHERN IRELAND"
gem2$NES13RNAME[gem2$NES13RNAME == "NETEHERLANDS"] <- "NETHERLANDS"

gali[,8] <- toupper(gali[,8])

gem_HC <- rename(gem, "info_venture_country_hq" = "NES15RNAME")

gem_HC1 <- rename(gem1, "info_venture_country_hq" = "NES14RNAME")

gem_HC2 <- rename(gem2, "info_venture_country_hq" = "NES13RNAME")

gali_NES <- left_join( gali, gem_HC,  by = "info_venture_country_hq")

gali_NES1 <- left_join(gali, gem_HC1, by = "info_venture_country_hq")

gali_NES1 <- filter(gali_NES1 , info_venture_country_hq == "UGANDA" | info_venture_country_hq == "EL SALVADOR")

gali_NES2 <- left_join(gali, gem_HC2, by = "info_venture_country_hq")

gali_NES2 <- filter(gali_NES2 , info_venture_country_hq == "ZAMBIA" | info_venture_country_hq == "GHANA" | info_venture_country_hq == "NIGERIA")

galiNES <- bind_rows(gali_NES, gali_NES1, gali_NES2)

countries_list <- galiNES %>% 
  group_by(galiNES$info_venture_country_hq) %>%
  summarize(Count=n()) %>%
  mutate(Percent = round((Count/sum(Count)*100))) %>%
  arrange(desc(Count))

```{r Merge with GEM APS data}
#APS0 <- import("GEM 2016 APS Global.sav")
APS <- APS0 %>% 
  select(suskill, country, ctryalp) %>%
  group_by(country) %>%
  summarise(skill_mean = mean(suskill, na.rm=TRUE))

APS <- rename(APS, "NES15COUNTRY" = "country")

gali_NESAPS <- merge(gali_NES, APS, by = "NES15COUNTRY")

countries_list <- filter(countries_list, Count > 25)

gali_GEM <- gali_NESAPS %>%
  filter(info_venture_country_hq  %in% countries_list$`gali_NES$info_venture_country_hq`)

```{r}
# Create dummy variables
gali_GEM$res_man <- ifelse(gali_GEM$most_important_benefit=="acc_managerial", 1, 0)
gali_GEM$res_fin <- ifelse(gali_GEM$most_important_benefit=="acc_financial_max", 1, 0)
gali_GEM$res_soc <- ifelse(gali_GEM$most_important_benefit=="acc_social_max", 1, 0)
gali_GEM$res_sig <- ifelse(gali_GEM$most_important_benefit=="acc_signaling", 1, 0)

#Renaming for plot purposes 
gali_GEM$info_venture_country_hq[gali_GEM$info_venture_country_hq == "UNITED STATES OF AMERICA"] <-"USA"

gali_GEM$info_venture_country_hq[gali_GEM$info_venture_country_hq == "UNITED KINGDOM OF GREAT BRITAIN AND NORTHERN IRELAND"] <-"UNITED KINGDOM"

gali_GEM_noUS <- filter(gali_GEM, info_venture_country_hq != "USA")

###ANALYSIS BASED ON GALI_GEM data to evaluate normative and cognitive differences and the impact of human capital as an acceleration resource

```{r}
#Summary table

#ls(gali_GEM)

#IV res_man Attention to human capital by the founders 
#DVs fins_revenues_m1 fu1-fins_revenues_m1 fins_revenues_sincefound

gali_GEM$y1_revenue <- gali_GEM$`fu1-fins_revenues_m1` - gali_GEM$fins_revenues_m1
gali_GEM$y1_ownmoeny <- gali_GEM$`fu1-inv_ownmoney_m1` - gali_GEM$inv_ownmoney_m1
gali_GEM$y1_aspiration_cap <- gali_GEM$fu1_tot_plans_cap_12m - gali_GEM$tot_plans_cap_12m
gali_GEM$y1_raised_cap <- gali_GEM$fu1_tot_cap_m1 - gali_GEM$tot_cap_m1

fu1-inv_plans_outequity_12months
fu1-inv_plans_outequity_3years
fu1_tot_plans_cap_12m

#Controls

fu1-report_any_prior_accelerator

#Revenue as a DV

revenue_lm_b <- lm(`fu1-fins_revenues_m1` ~ res_man, data = gali_GEM_noUS)
summary(revenue_lm_b)

revenue_lm <- lm(`fu1-fins_revenues_m1` ~ res_man + `fu1-report_any_prior_accelerator` + finished + fins_ft_employees_m1 ,
                 data = gali_GEM)
summary(revenue_lm)

revenue_lm_cog <- lm(`fu1-fins_revenues_m1` ~ res_man + res_man*skill_mean + `fu1-report_any_prior_accelerator` + fins_ft_employees_m1, data = gali_GEM)
summary(revenue_lm_cog)

revenue_lm_norm <- lm(`fu1-fins_revenues_m1` ~ res_man + res_man*ZNES15D2SUM9 +  res_man*skill_mean+ `fu1-report_any_prior_accelerator` + fins_ft_employees_m1+ finished, data = gali_GEM)
summary(revenue_lm_norm)
+ fins_ft_employees_m1 + finished

#Capital aspirations as a DV

lm_b <- lm(fins_revenues_m1  ~ receivedHC*res_man  , data = gali_GEM)

summary(lm_b)

lmOut(lm_b, file =  "results_asp22.csv")

ggplot(gali_GEM, aes(skill_mean, ZNES15D2SUM9, label= info_venture_country_hq))+
  geom_point(colour = "Light Blue")+
  geom_text(check_overlap = TRUE, size = 2.5, nudge_y = 0.1)+
  theme_minimal()+
  xlab("Cognitive acceptance")+
  ylab("Normative acceptance")

gali_GEM %>% 
  group_by(info_venture_country_hq) %>%
  summarise(mean(NES15D2SUM_MEAN9))

gali_GEM %>% 
  group_by(info_venture_country_hq) %>%
  summarise(mean(NES15_D01_MEAN9))

```{r fig.width=15}
ggplot(gali_GEM, aes(info_venture_country_hq))+
  geom_histogram(stat = "count")+
  theme(axis.text.x = element_text(angle = -80))

```{r Merge with VIMBI data}
vimbi <-  import("vimbi2017.xlsx") #211 obs
vimbi <- rename(vimbi, "info_venture_country_hq" = "Country: World Bank name")
vimbi <- clean_names(vimbi)

gali_vimbi <- merge(gali_0,vimbi, by = "info_venture_country_hq")

```{r}
# Create dummy variables
gali_vimbi$res_man <- ifelse(gali_vimbi$most_important_benefit=="acc_managerial", 1, 0)
gali_vimbi$res_fin <- ifelse(gali_vimbi$most_important_benefit=="acc_financial_max", 1, 0)
gali_vimbi$res_soc <- ifelse(gali_vimbi$most_important_benefit=="acc_social_max", 1, 0)
gali_vimbi$res_sig <- ifelse(gali_vimbi$most_important_benefit=="acc_signaling", 1, 0)

gali_vimbi <- filter(gali_vimbi, tot_cap_sincefound < 10000000)

#res_fe_mod <- lm(res_sig ~ x3_cp_capital_rank_percent_2016_h_good, 
                    #data = gali_vimbi)

vimbi$gni_capita_10_year_growth_2006_2015 <- as.numeric(vimbi$gni_capita_10_year_growth_2006_2015)

ggplot(gali_vimbi, aes(x=fins_revenues_sincefound, y=x1_lb_labour_flexibility_education_support_2016_h_good, colour=factor(res_sig))) +
  geom_point() +
  scale_x_log10()

hlm <- lmer(log1p(fins_revenues_sincefound)~1+(1|x1_lb_labour_flexibility_education_support_2016_h_good), gali_vimbi)

summary(hlm)

with(gali_vimbi, tapply(fins_revenues_sincefound, x1_lb_labour_flexibility_education_support_2016_h_good, mean))
coef(hlm)

dt_matrix <- cor(na.omit(vimbi[ ,3:8]))

cortest.bartlett(na.omit(vimbi[ ,3:8]))

det(dt_matrix)

pc1 <- principal(na.omit(vimbi[ ,3:8]), nfactors=3, rotate="none")
plot(pc1$values, type = "b")

efaMR(x=na.omit(vimbi[ ,3:8]), factors=3, covmat=NULL, n.obs=151, 
      dist='normal', fm='ols', rtype='orthogonal', rotation = 'CF-varimax', 
      input.A=NULL, additionalRC = NULL, 
      nstart = 100, compare = 'First', plot = T, cex = .5,
      normalize = FALSE, geomin.delta = .01, 
      MTarget = NULL, MWeight = NULL, PhiTarget = NULL, PhiWeight = NULL, 
      useorder = FALSE, mnames = NULL, fnames = NULL, wxt2 = 1)

bwplot(x1_lb_labour_flexibility_education_support_2016_h_good~resid(hlm), gali_vimbi)

```{r Clean data from for profit ventures that included philantropy in their capital structure }

#gali_0 <- filter(gali_0,pctphilan_sincefound == 0 )

```{r fig.width=15}
ggplot(gali_0, aes(info_venture_country_hq))+
  geom_histogram(stat = "count")+
  theme(axis.text.x = element_text(angle = -80))

>>>>

#load libraries
#if (!requireNamespace("BiocManager", quietly = TRUE))
#install.packages("caret")

@@

library(rio)
library(tidyverse)
library(lubridate)
library(janitor)
library(ggplot2)
library(readxl)
library(reshape2)
library(readr)
library(psych)
library(foreign)
library(plm)
library(lme4)
library(lattice)
library(lmerTest)
library(EFAutilities)
library(haven)
library(sjPlot)
library(XLConnect)
library(preprocessCore)
library(knitr)
library(caret)

@@

```{r Countries to analyse in main sample}
gali <- import("Data/GALI_External_DataRelease_2020.xlsx")

@@

#Removing countries with less than 6 ventures.

@@

countries_to_keep <- filter(countries_to_keep, Count >6)
countries_to_keep$`gali$info_venture_country_hq`

@@

#Number of ventures in main sample 
#kable(countries_to_keep)

```{r}
gali <- filter(gali, found_name1_age > 14 | is.na(found_name1_age))
gali <- filter(gali, found_name2_age > 14 | is.na(found_name2_age))
gali <- filter(gali, found_name3_age > 14 | is.na(found_name3_age))
gali <- filter(gali, found_name1_age < 70 | is.na(found_name1_age))
gali <- filter(gali, found_name2_age < 70 | is.na(found_name2_age))
gali <- filter(gali, found_name3_age < 70 | is.na(found_name3_age))

#Keep only ventures with 3 years of post acceleration information 
gali <- filter(gali, fu1report_followup_yes == 1 & fu2report_followup_yes == 1 & fu3report_followup_yes == 1)

@@

if (gali$application_year == 2013) { gali <- filter(gali, info_founding_year > 2007)
}  else if (gali$application_year == 2014) {gali <- filter(gali, info_founding_year > 2008)
} else if (gali$application_year == 2015) {gali <- filter(gali, info_founding_year > 2009)
}  else if (gali$application_year == 2016) {gali <- filter(gali, info_founding_year > 2010)
} else if (gali$application_year == 2017) {gali <- filter(gali, info_founding_year > 2011)
}  else gali <- filter(gali, info_founding_year > 2012)
```

```{r Countries to keep in sample with valid data}

gali <- gali %>%
  rename(country = info_venture_country_hq) %>%
  rename(year = program_year)

gali$country[gali$country == "United States of America"] <-"USA"
gali$country[gali$country == "Tanzania, United Republic of"] <-"Tanzania"

countries_to_keep <- gali %>% 
  group_by(gali$country) %>%
  summarize(Count=n()) %>%
  mutate(Percent = round((Count/sum(Count)*100))) %>%
  arrange(desc(Count))

countries_to_keep <- filter(countries_to_keep, `gali$country` != 'NA')

countries_to_keep <- filter(countries_to_keep, Count >6)
countries_to_keep$`gali$country`

gali <- gali %>%
  filter(country  %in% countries_to_keep$`gali$country`)

#Number of ventures in main sample 
#kable(countries_to_keep)
```

#GEM NES Data

```{r}
gem_nes <- import("Data/GEM-NES.csv")

#Clean and tidy gem NES
gem_nes <- clean_names(gem_nes)
gem_nes <- gem_nes %>%
  row_to_names(row_number = 2)

gem_nes[,-2] <- gem_nes[,-2] %>% mutate_if(is.character,as.numeric)

gem_nes$inst_hc_nes <- rowMeans(gem_nes[,(5:6)])
gem_nes <- clean_names(gem_nes)
gem_nes <- gem_nes %>%
  rename(country = economy) %>%
  rename(inst_fc_gem = 	financing_for_entrepreneurs)

gem_nes <- gem_nes [, -(5:6)]

#Normalize NES data (all data is based on a scale from 1 to 5)
preproc_nes <- preProcess(gem_nes[,(4:5)], method=c("range"))
gem_nes <- predict(preproc_nes, gem_nes)

#GEM APS data

```{r}
gem_aps <- import("Data/GEM-APS.csv")
#Clean and tidy gem APS
gem_aps <- clean_names(gem_aps)
gem_aps <- gem_aps %>%
  row_to_names(row_number = 2)
gem_aps[,-2] <- gem_aps[,-2] %>% mutate_if(is.character,as.numeric)
gem_aps <- clean_names(gem_aps)
gem_aps <- gem_aps %>%
  rename(country = economy) %>%
  rename(inst_signaling_aps = high_status_to_successful_entrepreneurs)%>%
  rename(inst_hc_aps = established_business_ownership) %>%
  rename(inst_sc_aps = total_early_stage_entrepreneurial_activity_tea)

#All APS data is a percentage. We devide by 100 to gat [0,1] range
gem_aps$inst_signaling_gem <- gem_aps$inst_signaling_aps /100
gem_aps$inst_hc_aps <- gem_aps$inst_hc_aps /100
gem_aps$inst_sc_gem <- gem_aps$inst_sc_aps /100

#Final GEM data

```{r}
#join nes and aps on country and year 
gem <- left_join(gem_nes, gem_aps, by=c("country", "year", "code"))
gem$inst_hc_gem <- rowMeans(gem[,c("inst_hc_nes", "inst_hc_aps")])

gem <- gem %>%
  select(code, country, year, ends_with('_gem'))

gem$country[gem$country == "United States"] <-"USA"

gem <- gem %>%
  group_by(country) %>%
  mutate(inst_fc_gem = mean(inst_fc_gem, na.rm= TRUE),
  inst_hc_gem = mean(inst_hc_gem, na.rm= TRUE),
  inst_sc_gem = mean(inst_sc_gem, na.rm= TRUE),
  inst_signaling_gem = mean(inst_signaling_gem, na.rm= TRUE))

gem <- select(gem, -year)

gem <- gem %>% distinct()

#CGI data
```{r}
gci <- import("Data/GCI_2018.xlsx")

gci <- filter(gci, `Series Global ID` == "EOSQ089" |
                   `Series Global ID` == "EOSQ425" )
gci <- filter(gci, Edition ==2018 )

gci <- filter(gci, Attribute == "VALUE")
gci <- select(gci, -c("Index", "Edition", "Freeze date", "Series units", "Series order", "Series code (if applicable)", "Attribute", "Series name"))

gci <- gci %>%
  gather(country, score, -`Series Global ID`)

gci$country[gci$country == "United States"] <-"USA"

gci <- gci %>%
  filter(country  %in% countries_to_keep$`gali$country`)

gci$score <- round(as.numeric(gci$score),2)

gci <- clean_names(gci)

gci <- gci %>%
  pivot_wider(names_from = series_global_id, 
              values_from = score)
preproc_gci <- preProcess(gci %>%
                            select(starts_with("EOSQ"))
                          , method=c("range"))
gci <- predict(preproc_gci, gci)

gci$inst_fc_gci <- rowMeans(gci[,c('EOSQ425','EOSQ089')], na.rm = TRUE)

gci <- select(gci, !starts_with('EOSQ'))

#Attention to capital - venture data

```{r}
#Rank 1 shows the most important benefit (highest attention)
#After normalizing, I will substract 1 and take absolute value to make sure higher value in range 0 to 1 goes to higher attention. This is to ensure that country and ventures variables move on the same directions, in order to construct a congurance level.

#Normalize Attention data (all data is based on a scale from 1 to 7)
preproc_gali <- preProcess(gali %>%
                            select(starts_with("accel_ben_rank_"))
                          , method=c("range"))
gali <- predict(preproc_gali, gali)

#Calculating the average of different benifits to group them into one of the 3 categories of capital plus signaling.

gali$attention_hc <- 1- round((rowMeans(gali[,
                                  c('accel_ben_rank_business_skills',
                                    'accel_ben_rank_mentorship')],
                              na.rm=TRUE)),2)

gali$attention_signaling <- 1- round((gali$accel_ben_rank_aware_cred),2)

gali$attention_sc <- 1- round((rowMeans(gali[,
                                  c('accel_ben_rank_network',
                                'accel_ben_rank_access_entreprene')],
                              na.rm=TRUE)),2)

gali$attention_fc <- 1- round((rowMeans(gali[,
                                c('accel_ben_rank_access_investors',
                                  'accel_ben_rank_direct_funding')],
                              na.rm=TRUE)),2)

#I will then mutiply this by the country index to measure the congruence level
```

#Join all 3 datasets 
```{r}
gali_joined <- left_join(gali, gem, by = "country")

gali_joined <- left_join(gali_joined, gci, by = "country")

#Checking if the two methods of measring institutional fc are correlated. We want them to be highly correlated 
cor(gali_joined$inst_fc_gem, gali_joined$inst_fc_gci, use="complete.obs")

#Panel data structure. Revenues in year t-1 as revenue 
```{r}
revenue_data <- select(gali_joined, starts_with('country') | starts_with("attention") | starts_with("inst") | ends_with("fins_revenues_m1") | ends_with("External_ID"))

revenue_data <- select(revenue_data, -fu4fins_revenues_m1)

revenue_data <- revenue_data %>% 
  gather(year, revenue, ends_with("fins_revenues_m1"))

revenue_data$year[revenue_data$year == "fins_revenues_m1"] <- -1
revenue_data$year[revenue_data$year == "fu1fins_revenues_m1"] <- 0
revenue_data$year[revenue_data$year == "fu2fins_revenues_m1"] <- 1
revenue_data$year[revenue_data$year == "fu3fins_revenues_m1"] <- 2

revenue_data$year <- as.numeric(revenue_data$year)

#Initial FE regression without controls 
```{r}
gali_fe_mod <- plm(revenue ~ (attention_fc*inst_fc_gci) , 
                   data = revenue_data, 
                   index = c("country", "year"),
                   model = "within")

@@

@@
